CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-10-01 codecheck-paper.tex
update text on R package, notes for related work

A custom R package, \texttt{codecheck}\footnote{
\url{https://github.com/codecheckers/codecheck}} helps with the generation
of certificates and depositing certificates and reated files on Zenodo 
using the R package \texttt{zen4R} \cite{zen4r}.
Codecheckers may choose to not use the package and rely on their own tools
for creating the certificate. This is a deliberate flexibility to
accomodate both different skill sets and unforseen technical advances or
challenges.

@@

>>>>

A custom R package, \texttt{codecheck}\footnote{
\url{https://github.com/codecheckers/codecheck}}, helps with the authoring
of certificates, and with the deposition of certificates and reated files to
Zenodo using the R package \texttt{zen4R} \cite{zen4r}.
Codecheckers may choose to not use the package and rely on their own tools
for creating the certificate. This is a deliberate flexibility to
accomodate both different skill sets and unforseen technical advances or
challenges.

@@

\url{https://twitter.com/Code_Copilot}

% first glimpse into "Code exeuction processes in scholarly publishing" ?
% `https://docs.google.com/document/d/1fMWrFvBTwAYXg5J_bYIjgb-gY7DfQ0DOjx9Vlg_Rbmg/edit# ?
